---
title: "Predicting probability of life satisfaction level among adult Canadians with multiple factors in life"
author: "Steven Tran, Nayoung Kim"
date: "October 19th 2020"
output: pdf_document
header-includes: 
    - \usepackage{tabularx}
    - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(survey)
library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)
library(gridExtra)
library(plot3D)
library(tab)
library(ggplot2)
```

## Abstract

This report analyzes how mature Canadians feel about their life, provided certain factors in life. Deriving data from the 2017 General Social Survey, this analysis utilizes a dependent variable that has two categorical levels- whether the respondent individual answered feeling generally happy, or the respondent was overall not content with life. Income of the respondent illustrated to play a role in influencing the life rating, whereas other factors in life did not portray a significance in affecting the rating. This was a meaningful discovery as higher income was found to be associated with higher life happiness level in general.   

## Introduction

Here is where you should give insight into the setting and introduce the goal of the analysis. Here you can introduce ideas and basic concepts regarding the study setting and the potential model. Again, this is the introduction, so you should be explaining the importance of the work that is ahead and hopefully build some suspense for the reader. You can also highlight what will be included in the subsequent sections.

The goal of this analysis is to discover a relationship between the outcome variable of contentedness of life and the auxiliary variables of factors in life by utilizing a logistic regression model. In this analysis, the study variable is feelings about life, and five auxiliary variables were selected to test if they indeed have a relationship with the outcome variable. Feelings about life were measured as generally happy if the rating was five or higher out of 10, while they were grouped as overall not content if the rating was lower than 5. The chosen dependent variables are age at first birth, current age of the respondent, income of the respondent, place of birth whether it is within or outside of Canada, and future intention of having any children. While there were numerous variables in the data that were available to select, these five specific variables were intuitively picked to check the hypothesis that these will have an association with life rating. The importance of the work is that through the logistic regression model, an analysis can be built about how adult individuals in Canada feel about their life, considering the input variables. More precisely, the probability of an adult Canadian having a contented life can be calculated. Ultimately, the main goal is to observe if any of these life factors affect life rating, and if so, how large the influence is. In the subsequent sections, the model section is covered and explained using tables and the results section through a graph, while weaknesses and next steps are also discussed.

## Data

Introduce the data, explain why it was selected. Make sure to comment on important features and highlight any potential drawbacks to the data.

<<<<<<< HEAD
The selected output variable is feelings about life, and the auxiliary variables are age of the respondent, age at first birth, place of birth (whether it was in Canada or not), income of the respondent, and intention of having future children. We chose this study variable in the intent to scrutinize the life satisfaction rating of Canadians, whether this is dependent on certain factors in life. Also, we decided on the specific input variables because intuitively, they are the most suitable data for our hypothesis and to prove that indeed, there is a relationship between the y and x variables. All of the data were pulled from the General Social Survey - Family (GSS) that was conducted in 2017. The 2017 survey data set was selected because it was a relatively recent set of data, therefore more interesting and purposeful to observe as it reflects comparatively newer and current responses. Survey data includes a target population of non-institutionalized individuals who are 15 years of age or older in the 10 provinces of Canada. The survey's primary objectives are to gather data on social trends to monitor changes in the living conditions of Canadians throughout life, and to provide information on specific social policy issues of current interest.
20,602 respondents had responded to the survey, and the number of respondents is also the sample size. This survey is a cross-sectional design and uses a two-stage sampling design. During the first stage, the sampling groups are the groups of telephone numbers, and the second stage units are people in the identified households. The sampling frame is Statistics Canada's common telephone frame, which combines landline and cellular telephone numbers that are from the Address Register. Survey data were collected through self-completed online questionnaires and telephone interviews, handled both in English and French. Since responding to the survey was voluntary, there were non-responses, and survey respondents were allowed to have non-responses within their survey answers as well. Also, although there were households without telephone services- generally, these exclusions are small, and so introduced biases were expected to be minor too. 
In the data set, there were numerous variables and responses, and some variables were very similar to one another. For instance, there were two questions regarding income, one for income of the respondent and another for income of the entire family. Since income of the respondent would usually be more direct and influential to the respondent, this variable was chosen instead of the other. There were no new variables that were constructed by combining multiple others, as each variable by itself normally had several response options, and it would be confusing to mix up the variables. The key features of the survey are that it covers various important life events and factors that influence life, and so the primary objectives of the survey are well covered and represented. Its strengths are that therefore, the survey is fairly accurate in terms of representing all the variables that affect life, and the large number of respondents and the appropriate survey designs also add to the accuracy of the survey. 
A drawback to the data is that because of the numerous questions and responses in the survey and gathered data, it was time consuming to review all these to choose our variables. Another drawback to the data is that there are numerous vague responses such as "Don't know" or "Unsure", which are difficult to place in order which should be placed before the other. Furthermore, some weaknesses about the survey in general are that the questions could have been phrased more inclusively, and that the answer options could have been broader. For example, the variable "age at first birth" does not include males, and all males responded with "NA" to the question. However, males are broadly still affected by first child's birth, as they participate in nurturing the child. A more precise question would be with the phrase "age at first child's birth," which would permit males to answer. Moreover, the variable "sex" only represents female or male- such option for "intersex" is not included. Perhaps another category could have been added for "gender," in which respondents could have more comfortably represented themselves within the LGBTQ+ group.    

## Model

Introduce the selected model here. It is expected that you will use some mathematical notation here. If you do please ensure that all notation is explained. You may also want to discuss any special (hypothetical) cases of your model here, as well as any caveats.


```{r include=FALSE, echo=FALSE, warning=FALSE}
=======
The selected output variable is feelings about life, and the auxiliary variables are age of the respondent, age at first birth, place of birth (whether it was in Canada or not), income of the respondent, and intention of having future children. We chose this study variable in the intent to scrutinize the life satisfaction rating of Canadians, whether this is dependent on certain factors in life. Also, we decided on the specific input variables because intuitively, they are the most suitable data for our hypothesis and to prove that indeed, there is a linear relationship between the y and x variables. A drawback to the data is that because of the numerous 'NA' responses, our population data size greatly decreased from the original sampled population number. Another drawback to the data is that there are numerous vague responses such as "Don't know" or "Unsure", which are difficult to place in order.

```{r}
>>>>>>> 77e90a84d97cc3faaacf7286d58454fe3fe900c4
can_pop_stats <- read.csv("popstats.csv", nrows=15) %>% 
    select(province=Geographic.name, population=Population..2016) %>% 
    filter(!(province %in% c("Canada", "Yukon", "Northwest Territories", "Nunavut", "")))

gss_full <- read.csv("gss.csv")

#gss = gss_full %>% # Select only the variables that are used in our model
#    select(c(
#             province,
#             feelings_life,
#             age,
#             income_respondent,
#             place_birth_canada,
#             age_at_first_birth,
#             future_children_intention)) %>% drop_na
gss_full$future_children_intention[is.na(gss_full$future_children_intention)] <- "Don't know"
gss = gss_full %>% # Select only the variables that are used in our model
    select(c(
             province,
             feelings_life,
             age,
             income_respondent,
             place_birth_canada,
             age_at_first_birth,
             future_children_intention)) %>%
replace_na(list(
                "",
                0, 
                0,
                "Less than $25,000",
                "Don't know",
                0,
                "Don't know"
                )) %>%
drop_na() # Remove the NA values

# Perform inner join on 'province' for finite population correction
gss <- inner_join(gss, can_pop_stats, by="province")

# Convert some columns we'll be using as dummy variables to be ordered factors
gss$income_respondent <- factor(gss$income_respondent, levels=c(
    "Less than $25,000",
    "$25,000 to $49,999",
    "$50,000 to $74,999",
    "$75,000 to $99,999",
    "$100,000 to $ 124,999",
    "$125,000 and more"
))
gss$place_birth_canada <- factor(gss$place_birth_canada, levels=c(
    "Don't know",
    "Born outside Canada",
    "Born in Canada"
))
gss$future_children_intention <- factor(gss$future_children_intention, levels=c(
    "Don't know",
    "No, definitely not",
    "Probably not",
    "Unsure",
    "Probably yes",
    "Definitely yes"
))
```


```{r, fig.width=10, fig.height=12}
feels_hist <- ggplot(data=gss, aes(x=feelings_life)) + 
    geom_histogram(bins=30) + 
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    ggtitle("Figure 1: Distribution of feelings_life")
age_hist <- ggplot(data=gss, aes(x=age)) + 
    geom_histogram(bins=30) + 
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    ggtitle("Figure 2: Distribution of age")
age_birth_hist <- ggplot(data=gss, aes(x=age_at_first_birth)) + 
    geom_histogram(bins=30) + 
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    ggtitle("Figure 3: Distribution of age_at_first_birth")

income_bar <- ggplot(data=gss, aes(x=income_respondent)) + 
    geom_bar() + 
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    ggtitle("Figure 4: Distribution of income_respondent")
birth_can_bar <- ggplot(data=gss, aes(x=place_birth_canada)) + 
    geom_bar() + 
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    ggtitle("Figure 5: Distribution of place_birth_canada")
child_int_bar <- ggplot(data=gss, aes(x=future_children_intention)) + 
    geom_bar() + 
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    ggtitle("Figure 6: Distribution of future_children_intention")
grid.arrange(grobs=list(feels_hist, 
                        age_hist,
                        age_birth_hist, 
                        income_bar, 
                        birth_can_bar, 
                        child_int_bar), 
             ncol=2)

gss_means <- gss %>% group_by(province) %>% summarise_at(vars(-future_children_intention, -place_birth_canada, -income_respondent), mean)
prov_feels <- ggplot(data=gss_means, aes(x=province, y=feelings_life)) + 
    geom_point() + 
    theme(axis.text.x=element_text(angle=45, hjust=1), plot.title=element_text(hjust=0.5)) +
    ggtitle("Figure 7: Mean feelings_life by province") +
    ylab("Mean feelings_life")
prov_age <- ggplot(data=gss_means, aes(x=province, y=age)) + 
    geom_point() + 
    theme(axis.text.x=element_text(angle=45, hjust=1), plot.title=element_text(hjust=0.5)) +
    ggtitle("Figure 8: Mean age by province") +
    ylab("Mean age")
prov_age_birth <- ggplot(data=gss_means, aes(x=province, y=age_at_first_birth)) + 
    geom_point() + 
    theme(axis.text.x=element_text(angle=45, hjust=1), plot.title=element_text(hjust=0.5)) +
    ggtitle("Figure 9: Mean age_at_first_birth by province") +
    ylab("Mean age_at_first_birth")
grid.arrange(grobs=list(prov_feels, prov_age, prov_age_birth), ncols=3)
```

```{r, fig.width=10, fig.height=6}
scatter3D(
          x=as.numeric(gss$age_at_first_birth), 
          y=as.numeric(gss$age), 
          z=as.numeric(gss$feelings_life), 
          bty="b2", 
          theta=50, 
          phi=30, 
          cex=0.5,
          font=0.8,
          main="Figure 10: Age at First Birth & Age vs Feelings About Life",
          xlab="Age at First Birth", 
          ylab="Age", 
          zlab="Feelings about Life"
)
```


## Model

Introduce the selected model here. It is expected that you will use some mathematical notation here. If you do please ensure that all notation is explained. You may also want to discuss any special (hypothetical) cases of your model here, as well as any caveats.

To predict the probability of a person being happy, which we define as:
$$ \text{Prob}(h):= \begin{cases}1, &\text{if feelings\_life}\geq 6 \\ 0, &\text{otherwise}\end{cases} $$
we fit a logistic regression model with some independent/predictor variables.

```{r}
data.frame(
           gss$income_respondent %>% sort %>% unique,
           gss$future_children_intention %>% sort %>% unique,
           c(as.vector(gss$place_birth_canada %>% sort %>% unique), rep("", 3))
           ) %>% kable(col.names=c(
                                   "Income of Respondent",
                                   "Future Children Intention",
                                   "Born in Canada?"
                                   ),
                       caption="Categorical Variables") %>% column_spec(1:3) %>% kable_styling(
                       latex_options="hold_position"
)
```

The other predictor variables are `age_at_first_birth` and `age`.

```{r, include=FALSE, warning=FALSE, echo=FALSE}
gss <- gss %>% mutate(happy=feelings_life>=6)
gss$feelings_life <- as.factor(gss$feelings_life)
gss.design <- svydesign(data=gss, ids=~1, strata=gss$province, fpc=gss$population)

model <- svyglm(happy ~
                age_at_first_birth +
                age +
                as.factor(income_respondent) +
                as.factor(place_birth_canada) +
                as.factor(future_children_intention),
            gss.design,
            family=quasibinomial
)
```
Using the GSS data, we replicated the approach used in the original survey. A single-stage stratified sampling approach by applying finite population correction to the sample was employed, adjusting each observation by the corresponding provincial population to reduce the variation. Then, we fitted a logistic model to the survey design, yielding the following model:
\begin{align*}
    \log \left(\frac{h}{1-h}\right) =\ &\beta_0 + \beta_1x_1 + \beta_2x_2 \\
    +\ &\underbrace{\beta_{3a}x_{3a} + \beta_{3b}x_{3b} + \beta_{3c}x_{3c} + \beta_{3d}x_{3d} + \beta_{3e}x_{3e}}_{\text{dummy coding for income}} \\
    +\ &\underbrace{\beta_{4a}x_{4a} + \beta_{4b}x_{4b}}_{\text{dummy coding for place birth Canada}} \\
    +\ &\underbrace{\beta_{5a}x_{5a} + \beta_{5b}x_{5b} + \beta_{5c}x_{5c} + \beta_{5d}x_{5d} + \beta_{5e}x_{5e}}_{\text{dummy coding for future children intention}}
\end{align*}
The functional form of the logistic model gives the logarithm of the odds of the outcome variable -- in this case, the binary variable `happy` ($h$). For each of the categorical variables in Table 1, we use dummy variable coding with the variable at the top representing the baseline, in order to be able to assess what effect, if any, moving to a category would have compared to the baseline. 

## Results

<!--Here you will include all results. This includes descriptive statistics, graphs, figures, tables, and model results. Please ensure that everything is well formatted and in a report style. You must also provide an explanation of the results in this section. You can overflow to an Appendix if needed. 

Please ensure that everything is well labelled. So if you have multiple histograms and plots, calling them Figure 1, 2, 3, etc. and referencing them as Figure 1, Figure 2, etc. in your report will be expected. The reader should not get lost in a sea of information. Make sure to have the results be clean, well formatted and digestible.-->
The coefficients fitted using the logistic regression model are given in Table 2. The *OR* column gives the odds ratio, *Beta (SE)* gives the logarithm of the odds ratio and corresponding standard error of the estimate. *P* gives the p-value for the significance test which evaluates the probability of encountering data as or more significant than the Wald test statistic.

```{r}
model_summary <- model %>% tabglm(columns=c("or", "beta.se", "p"), latex=T)
rownames(model_summary) <- c(
                             "$\\hfill\\beta_0$",
                             "$\\hfill\\beta_1$",
                             "$\\hfill\\beta_2$",
                             "income cat. var",
                             "income baseline",
                             "$\\hfill\\beta_{3a}$",
                             "$\\hfill\\beta_{3b}$",
                             "$\\hfill\\beta_{3c}$",
                             "$\\hfill\\beta_{3d}$",
                             "$\\hfill\\beta_{3e}$",
                             "birthplace cat. var",
                             "birthplace baseline",
                             "$\\hfill\\beta_{4a}$",
                             "$\\hfill\\beta_{4b}$",
                             "children int. cat. var",
                             "children int. baseline",
                             "$\\hfill\\beta_{5a}$",
                             "$\\hfill\\beta_{5b}$",
                             "$\\hfill\\beta_{5c}$",
                             "$\\hfill\\beta_{5d}$",
                             "$\\hfill\\beta_{5e}$"
)
model_summary$Variable <- model_summary$Variable %>% str_replace_all("_", "\\\\_")
model_summary$Variable <- model_summary$Variable %>% str_replace_all("\\$", "\\\\$")
model_summary %>% kable(row.names=T, escape=F, caption="Logistic Regression Model Summary") %>% kable_styling(latex_options="HOLD_position")
```
The model has the following interpretations:

- The intercept term has no meaningful interpretation and it is statistically significant with a very small p-value.
- The continuous variables `age_at_first_birth`, `age` very slightly affect the model with odds-ratios slightly off from 1.
- The categorical variables `place_birth_canada` and `future_children_intention` make a large difference to the odds ratio with odds-ratios near 0, but this is probably due to a flaw in the survey design which we will discuss in the Weaknesses section of this report.
- `income_respondent` is a meaningful variable in this model. For all six levels, the odds ratio is greater than 1 which implies that each increase in the respondent's income results in an increase in the log odds of being happy compared to the baseline.

Using a variety of parameters with this model, we obtain the following histogram that shows the class distribution of happiness.

```{r, fig.width=10, fig.height=3}
or_probs <- as.data.frame(predict(model, type="response"))
ggplot(or_probs, aes(x=response)) + 
    geom_histogram(bins=30) +
    ggtitle("Predicted Distribution of Happiness") + xlab("Probability of Being Happy")
```

## Discussion

<!--Here you will discuss conclusions drawn from the results and comment on how it relates to the original goal of the study (which was specified in the Introduction).-->



# Weaknesses

<!--Here we discuss weaknesses of the study, data, analysis, etc. You can also discuss areas for improvement.-->

# Next Steps

<!--Here you discuss subsequent work to be done after this report. This can include next steps in terms of statistical analysis (perhaps there is a more efficient algorithm available, or perhaps there is a caveat in the data that would allow for some new technique). Future steps should also be specified in terms of the study setting (eg. including a follow-up survey on something, or a subsequent study that would complement the conclusions of your report).-->



## References

Bibliography:

1. General Social Survey: An Overview, 2019. (2019, February 20). Retrieved October 12, 2020, from Statistics Canada, Canada website:  https://www150.statcan.gc.ca/n1/pub/89f0115x/89f0115x2019001-eng.htm

2. General Social Survey - Family (GSS). (2019, February 7). Retrieved October 12, 2020, from Statistics Canada, Canada website: https://www23.statcan.gc.ca/imdb/p2SV.pl?Function=getSurvey&SDDS=4501

3. Population and Dwelling Count Highlight Tables, 2016 Census. (2019, February 20). Retrieved October 17, 2020, from Statistics Canada, Canada website: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/hlt-fst/pd-pl/Table.cfm?Lang=Eng&T=101&S=50&O=A

4. Wu, Changbao, and Mary E. Thompson. "Basic Concepts in Survey Sampling." Sampling Theory and Practice. Springer, Cham, 2020. 3-160.
